\secHeader{Conferences, Workshops, \& Seminars}

\begin{longtable}[l]{@{} m{2.5mm} m{18.25cm}}

% \diamond &\textbf{Departmental Seminar, February 2026}\hfill St. Xavier's College, Kolkata\\*
% &Contribution: Oral presentation (Invited)\\[0.2cm]


\diamond &\textbf{Brain Network Dynamics Meeting (BraiNDy) 2026}\hfill Udaipur, India\\*
&Contribution -- Oral presentation (Invited), Conference organisation. \\[0.2cm]

\diamond &\textbf{Five-day Workshop on Complex Network Analysis with Applications 2025}\hfill IIIT Kottayam\\*
&Contribution: Oral presentation (Invited). \\[0.2cm]

\diamond &\textbf{Regional Young Investigators' Meeting (RYIM) 2024-25}\hfill NBRC Gurgaon \& Ashoka Univ., New Delhi\\*
&Contribution: Poster presentation. \\[0.2cm]


\diamond &\textbf{Brain Network Dynamics Meeting (BraiNDy) 2024}\hfill Ashoka Univ., New Delhi\\[0.2cm]

\diamond &\textbf{WINQ Program on Complex and Quantum Systems 2024}\hfill NORDITA, Stockholm\\*
&Contribution: Oral presentation. \\[0.2cm]

\diamond &\textbf{Perspectives in Nonlinear Dynamics (PNLD) 2023}\hfill IIT Madras \\*
&Contribution: Poster presentation, Conference organisation. \\[0.2cm]

\diamond &\textbf{Mediterranean School of Complex Networks (MSCx Networks) 2023}\hfill Catania, Italy \\[0.2cm]

\diamond &\textbf{International Nonlinear Dynamics Conference (NODYCON) 2023}\hfill Sapienza Univ. of Rome\\*
&Contribution: Oral presentation. \\[0.2cm]

\diamond &\textbf{Symposium on Epidemic Modelling (EpiSym) 2022}\hfill IIT Madras \\*
&Contribution: Conference organisation. \\[0.2cm]

\diamond &\textbf{NSM Workshop on High-Performance Computing 2022}\hfill IIT Bombay \\[0.2cm] 

\diamond &\textbf{Conference on Complex Systems (CCS) 2021}\hfill Lyon, France\\*
&Contribution: Oral presentation (online). \\[0.2cm]

\diamond &\textbf{Conference on Nonlinear Systems and Dynamics (CNSD) 2019}\hfill IIT Kanpur \\*
&Contribution: Poster presentation. \\[0.2cm]

\diamond &\textbf{ACM Winter School on HPC 2019}\hfill IIT Kanpur\\[0.2cm]

\diamond &\textbf{National Summer School on Statistical Physics 2018}\hfill SNBNCBS, Kolkata\\[0.2cm]
\end{longtable}

\vspace{0.35cm}